Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-22 windheat.tex
editing

\subsection{Over Star Formation History}
Generalizing to an arbitrary star formation history $S(t)$, the total rate of mass and energy input can be written as
\begin{align} 
  \dot{M}(t) &= \int_0^t S(t_1) \dot{\bar{m}}(t-t_1){\rm
      d}t_1\\
  \dot{E}(t) &= \int_0^t S(t_1) \dot{\bar{e}}(t-t_1){\rm
      d}t_1,\\
\end{align}
resulting in an effective wind heating rate of
\begin{align}
  v_w^2(t) &=2 \dot{E}(t)/\dot{M}(t)
\end{align}

\begin{figure}
\includegraphics[width=\columnwidth]{vw.pdf}
\caption{\label{NickPlot2} Effective wind velocities $V_{\rm w}$ for
different $S(t)$.  The yellow and orange curves are the Moster SF
histories, with and without Type II SNe, respectively.  The red,
purple, and blue curves are Moster SFs convolved with a $\sin^2(t)$
function normalized to $10^7$, $10^8$, and $10^9$ yr fluctuations,
respectively.  These solid curves lack SN, but the dashed purple curve
possesses it.  Effective $V_{\rm w}$ is strongly diminished when the
variability timescale is greater than $\sim$ twice the duration of
high-velocity winds.}
\end{figure}

>>>>

\subsection{Over Star Formation History}
Generalizing to an arbitrary star formation history $S(t)$, the total rate of mass and energy input can be written as
\begin{align} 
  \dot{M}(t) &= \int_0^t S(t_1) \dot{\bar{m}}(t-t_1){\rm
      d}t_1\\
  \dot{E}(t) &= \int_0^t S(t_1) \dot{\bar{e}}(t-t_1){\rm
      d}t_1,\\
\end{align}
resulting in a wind heating parameter of 
\begin{align}
  v_w^2(t) &=2 \dot{E}(t)/\dot{M}(t).
\end{align}

The mass return parameter will be

\begin{align}
\eta = \frac{\dot{M}(t)}{\int_0^t S(t_1) {\rm d}t_1} \th
\end{align}

% \begin{figure}
% \includegraphics[width=\columnwidth]{vw.pdf}
% \caption{\label{NickPlot2} Effective wind velocities $V_{\rm w}$ for
% different $S(t)$.  The yellow and orange curves are the Moster SF
% histories, with and without Type II SNe, respectively.  The red,
% purple, and blue curves are Moster SFs convolved with a $\sin^2(t)$
% function normalized to $10^7$, $10^8$, and $10^9$ yr fluctuations,
% respectively.  These solid curves lack SN, but the dashed purple curve
% possesses it.  Effective $V_{\rm w}$ is strongly diminished when the
% variability timescale is greater than $\sim$ twice the duration of
% high-velocity winds.}
% \end{figure}
